Elastic Scattering in General Relativistic Ray Tracing for Neutrinos

### 2018-06-14 paper.tex
Add a few acknowledgements, and clean up that language

\subsubsection*{Acknowledgements}
This research is supported in part by the Joint Institute for Nuclear
Astrophysics---Center for the Evolution of the Elements (JINA-CEE)
and the National Science Foundation under grant numbers \lstinline{X} (MBD),
by NASA through the Hubble Fellowship under grant \lstinline{51344.001-A},
awarded by the Space Telescope Science Institute,
which is operated  by the Association of Universities for Research in Astronomy, Inc.,
for NASA under contract \lstinline{NAS 5-26555} (EO),
and through the U.S.\ Department of Energy, Office of Science, Office of Nuclear Physics,
under award number \lstinline{DE-FG02-02ER41216} (GCM).
\footnote{TODO (Matt, Francois): grant nos?}
We thank Sherwood Richers for providing his neutrino transport code
\lstinline{Sedonu} for comparisons,
Fran\c{c}ois H\'{e}bert for his timely help in finding and
correcting bugs in the time-interpolation algorithm,
and Luke Roberts for helpful discussions.

>>>>

\subsubsection*{Acknowledgements}
This work was supported in part by the National Science Foundation under Grant
No.\ \lstinline{PHY-1430152} (JINA Center for the Evolution of the Elements)
[MBD, YLZ, GCM];
by NASA through the Hubble Fellowship under grant \lstinline{51344.001-A},
awarded by the Space Telescope Science Institute,
which is operated  by the Association of Universities for Research in Astronomy Inc.\
for NASA under contract \lstinline{NAS 5-26555} [EO];
and through the U.S.\ Department of Energy, Office of Science,
Office of Nuclear Physics,
under award number \lstinline{DE-FG02-02ER41216} [GCM].
We thank the Spectral Einstein Code collaboration
\footnote{\url{https://www.black-holes.org/code/SpEC.html}} for a powerful and
robust numerical relativity code base, and in particular
Lawrence E.\ Kidder, Daniel A.\ Hemberger, Fran\c{c}ois H\'{e}bert,
and Fatemeh Hossein Nouri for comments and help throughout.
We also thank Sherwood Richers for providing his neutrino transport code
\lstinline{Sedonu} for comparisons,
and Luke Roberts for helpful discussions at the JINA-CEE Frontiers meeting 2017.
